What's in a Domain?: Feature Engineering for URLs

### 2022-09-17 paper/paper.tex
Literature review

@@

\subsection{Data}
The data used in this study was collected from a wide range of advertisers running
broadly targeted campaigns between February and March 2022. It includes brands in
the automotive, retail, travel and health services verticals.
The data is broken into two one week time periods, the raw data was filtered
such that we had impressions for every creative in both
periods of time. This was a requirement of our approach so that we can
study the continuity of the relationships between creative, context and attention
across time.

In the analysis that follows we apply different levels of aggregation to the
log level impression data, so that we calculate the mean attention time for
a given creative in the specific context. Within each experiment we will
filter the aggregated data to ensure that every sample point is derived from
a least 50 impressions. This is done to ensure robust estimates of mean attention within
a given category.
Summary statistics for the dataset are shown in Table \ref{tab:dataset}. Note, that
due to the restriction outlined above, not every sample point will be in all experiemnts.

\begin{table}
\caption{Dataset of Attention Measured Impressions}
\label{tab:dataset}
\begin{tabular}{|l|r|r|}
\toprule
Metric          &Feb 18 - 24    &Feb 25 - March 03          \\
\midrule
Impressions     &16,895,661     &10,488,816     \\
URLS            &26,006         &27,855         \\
Domains         &2,263          &2,585          \\
Creatives       &683            &683            \\
Advertisers     &59             &59             \\
\bottomrule
\end{tabular}
\end{table}

@@

In order to derive contextual categories for each record in our dataset,
we applied the Verity API (\citeauthor{verity}) to the URLs. We converted the results of
the API response into a variety of features that describe the contextual
categories derived from the iAB V2.0 hierarchy \cite{iabv2}.

We identified the iAB category for which Verity had returned the
highest score and converted that category into a set of labels for
classification across the four Tiers of iAB V2.0. In instances where the
classified category is from a higher position in the hierarchy, then the
lower level tiers are given the deepest category. For example, if we have
a URL that is classified as iABv2 category "Business and Finance"
(a Tier 1 category) then Tiers 2, 3 and 4 will also contain the same value.

@@

\begin{figure*}
\includegraphics[scale=0.6]{../ranking_analysis/results/iABv2/no_url_repeat.png}
\caption{Expected Lift in Attention Time on Inventory without Repeated URLs.}
\label{fig:no_url}
\end{figure*}

We show the change in attention lift across the dimensions of iAB Tiers and category ranking
in Figure \ref{fig:no_url}. This figure demonstrates the increased performance with the specificity
of the iAB Tiers and the reduction in performance with the movement down category ranks.

@@

We show the change in attention lift across the dimensions of iAB Tiers and category ranking
in Figure \ref{fig:no_dom}. This figure demonstrates that in the no domain repeat experiment
we get a very similar overall pattern to the previous experiment. The primary difference
being a higher expected lift at the rank one position, and a faster drop off in expected
lift as we move down the ranks.

\begin{figure*}
\includegraphics[scale=0.6]{../ranking_analysis/results/iABv2/no_dom_repeat.png}
\caption{Expected Lift in Attention Time on Inventory without Repeated Domains.}
\label{fig:no_dom}
\end{figure*}

@@

\subsection{Significance Tests}

We estimated p-values for the significance of the proportion of URLs within a given category
that outperform the baseline. We did this using a binomial distribution, under the null model
assumption that the relationship between the attention on a URL and its contextual category
is random. Hence, the p-value can be estimated as the probability of obtaining the observed
number of successful improvements over the baseline as samples from a binomial with a probability
of success equal to $0.5$.

The computed p-values were extremely small, starting at $10^{-62}$ for first rank of Tier 1 in
the \emph{No URL Repeats} experiment, $10^{-24}$ for the \emph{No Domain Repeats} experiment.
The p-values increase gradually as we move down the ranking of the categories or at deeper
levels in the iAB hierarchy, but they always remain below a significance level
of 0.05.

A more stringent analysis would apply a Bonferroni correction to account for the multiple
hypothesis tests in these tables of data. Even with this correction, the vast majority
of results
are many orders of magnitude below the significance threshold. However, under this criteria
we would reject the third ranking category within the \emph{No Domain Repeats} experiments.
However, as the observed data is overwhelmingly statistically significant, and these values
are consistent with the hypothesis being true, but suffering from a diminishing effect size,
and reduced sample sizes, we included the values for the third ranking categories in the
table.

\section{Conclusion}
The pattern we observe is consistent between the two experiments. Regardless of
how novel the inventory is, there is a tendency for media sharing the top contextual
categories from the
initial period to consistently outperform the baseline attention.
This pattern is strongest with the number one category, and then recedes
as we progress down the ranking of categories from the first period.

Similarly, the bottom performing category from the first period consistently under performs
the baseline in the subsequent period, regardless of whether you are looking at new URLs
on existing domains, or entirely new domains.
These results strongly suggest that the topics discussed on pages in which an ad appears
interact with ad creatives in a way that enables prediction of ad attention.

As we move deeper into the hierarchy from Tier 1 down to Tier 4 we see that the average size
of the improvement increases, but this effect appears to plateau at Tier 3. We note that this
improvement would often be countered by reduced inventory volumes, suggesting that application
of these results will require weighting the gains against potential reach.

When we look at inventory on novel domains we see that there is a further small drop in the
proportion of instances where the category continues to deliver improved results. This is
countered by an improvement in the gain for the top performing category, suggesting that a
reasonable and risk efficient strategy for finding new inventory is to target multiple top
ranking categories on known websites, but just the top ranking category on novel websites.

Overall, these results provide strong evidence that attention measurement provides a signal
as to whether a given contextual targeting strategy is aligned with an advertising creative.
Performance, in terms of attention garnered, in an initial period is predictive of
attention in a future period even when the specific media changes.
The reliability of attention on new URLs or domains within the same contextual category
suggests that the iAB hierarchy provides insight into factors that align advertising
creatives with consumer psychology beyond the specifics of a particular media platform.

\section{Acknowledgments}
This research was financially supported by Playground XYZ and Gumgum.
The content benefited from commentary and observations made by Rob Hall.

\bibliographystyle{ACM-Reference-Format}
\bibliography{../bibliography/refs}

>>>>

Litrature review

Write a literature review \cite{Vazhayil2018}
\cite{Canali2011}
\cite{Ayes2019}
\cite{Mamun2016}
\cite{Li2020}
\cite{Basnet2012}
\cite{Basnet2014}
\cite{Tupsamudre2019}
\cite{Le2018}
\cite{Baykan2009}
\cite{Kan2005}
\cite{Hernandez2012}
\cite{Chung2022}
\cite{Qiu2020}
\cite{Vaishnavi2021}
\cite{Xu2021}
\cite{Rhea2022}

@@

\subsection{Data}

The data used in this study was collected from a collction of publications that 
present internet classification problems containing URLs as a key, or sole feature.
Malcious URL classification \cite{Mamun2016}.

\begin{table}
\caption{Datasets}
\label{tab:dataset}
\begin{tabular}{|l|r|r|}
\toprule
Metric          &Feb 18 - 24    &Feb 25 - March 03          \\
\midrule
Impressions     &16,895,661     &10,488,816     \\
URLS            &26,006         &27,855         \\
Domains         &2,263          &2,585          \\
Creatives       &683            &683            \\
Advertisers     &59             &59             \\
\bottomrule
\end{tabular}
\end{table}

@@

Verity had returned the
highest score and converted that category into a set of labels for
classification across the four Tiers of iAB V2.0. In instances where the
classified category is from a higher position in the hierarchy, then the
lower level tiers are given the deepest category. For example, if we have
a URL that is classified as iABv2 category "Business and Finance"
(a Tier 1 category) then Tiers 2, 3 and 4 will also contain the same value.

@@

@@

@@

\section{Conclusion}

\section{Acknowledgments}

\bibliographystyle{ACM-Reference-Format}
\bibliography{refs}
